### 2021-07-19 doc/thesis/chapters/system-design-process.tex
integrate

>>>>

This step combines multiple single components into a larger, integrated system, which can then be treated as a whole.
In order to be able to do that, interfaces between the components and subsystems need to be defined.
Optimally, these interfaces are designed in a way that the amount of data that needs to be exchanged is kept to a minimum.
It is of advantage, if a subsystem only transfers finished products that it produced to another subsystem.
The aim to develop simple interfaces is of special advantage in systems that include a feedback loop.
There, managing the feedback loop connections is easier if there is a clear interface, so the loop can be connected around an entire subsystem, instead of interconnecting within the subsystems.
